% Original Template Author: Rishi Shah

% Document Configuration
\documentclass{resume}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jack Gisby}
\address{Address: Available on Request \\ DOB: 28/02/1998}
\address{Tel: (+44)7748 559964 \\ Email: jackgisby@gmail.com \\ Github: https://github.com/jackgisby}

% Document Content 
\begin{document}
\begin{rSection}{Research Interests}
PhD candidate at Imperial College London with a keen interest in data-driven research and the omics technologies. I have the aspiration to pursue a career in biological research, exploiting the vast datasets produced by modern biology to answer fundamental research questions.

\end{rSection}
\begin{rSection}{Education}

{\bf Imperial College London} \hfill {\em August 2020 - Present} 
\\ PhD Candidate \hfill {Department of Immunology and Inflammation} \smallskip \\
I have begun applying an integrative transcriptomic and proteomic approach to investigate coronavirus disease 2019 (COVID-19) and systemic lupus erythematosus (SLE). 
\\

{\bf University of Birmingham} \hfill {\em September 2016 - July 2020} 
\\ Biochemistry with Professional Placement (MSci) \hfill {Current Average: 74\%} \smallskip \\
Key Modules: Gene Expression Analysis, Genetics, Research and Funding, Experimental Design and Analysis. Significantly improved my statistical and programming skills while gaining a background in molecular biology, physiology and genetics. Current coursework covers the processing of proteomic and transcriptomic datasets. \smallskip \\ Dissertation project involves the development and validation of the freely-available computational workflow, \textit{Metaboverse}.  \\

\end{rSection}
\begin{rSection}{Research Experience}

\begin{rSubsection}{Dissertation: A Prior Knowledge-Based Computational Workflow for \textit{de novo} Structural Elucidation of Small Molecules in Mass Spectrometry Metabolomics}{}{Dr Ralf Weber}{October 2019 - Present}

\item Developed my understanding of databases, data structures and algorithms for the optimisation of \textit{Metaboverse}; learned about NP-complete problems, graph theory and combinatorial optimisation for the representation and efficient generation of potential small molecules. 
\item Processed large, high-dimensional mass-spectrometry datasets for the validation of \textit{Metaboverse}. 
\item Used Python, SQLite and Bash to implement the \textit{Metaboverse} workflow  on a Linux high-performance computing cluster for the generation of large structure databases. 
\end{rSubsection}

\begin{rSubsection}{Summer Project: An Automated Tool for \textit{de novo} Annotation of Pack-TYPE Non-Autonomous Transposable Elements}{}{Dr Marco Catoni}{August 2019 - Present}

\item Designed and implemented a software package, written in R, to automatically detect Pack-TYPE transposable elements in \textit{Arabidopsis thaliana} and related species. 
\item Learned to use version control (Git) for the management of programming projects.
\item Adhered to Comprehensive R Archive Network (CRAN) and Bioconductor standard practices for the organisation, testing and documentation of packages.
\item Used command line and Bioconductor tools to process sequence data for \textit{Arabidopsis thaliana}, \textit{Oryza sativa} and related organisms.
\item Incorporated unsupervised machine learning approaches for the automated clustering of related transposable elements.
\item The package is currently being used by geneticists at the University of Birmingham to understand how Pack-TYPE transposons may impact evolution; the tool is available on Bioconductor for researchers interested in these dynamic elements.
\end{rSubsection}

\begin{rSubsection}{Placement Project: Development of an Immunoturbidimetric Assay for Serum Amyloid A for an Automated Clinical Analyser}{}{The Binding Site Group Ltd, Birmingham, UK}{August 2018 - August 2019}

\item Developed an assay for inflammatory biomarkers, such as Serum Amyloid A, for use in clinical laboratories. 
\item Took responsibility for a long term project that improved my interpersonal skills, allowed me to take ownership of a research project and developed my ability to work autonomously.
\item Interacted with, and regularly delivered presentations to, researchers from diverse fields and non-scientific staff to ensure the timely completion of my development project. 
\item Routinely used Excel, and statistical packages such as Analyse-It/Minitab, to analyse and present data to co-workers and managers. Took responsibility for planning and carrying out experiments and statistical analyses in a research environment. 
\item Received training in scientific writing in order to routinely produce experimental write-ups for submission to regulatory bodies; this involved compliance to standard operating procedures.
\item Produced an extended literature review and project report before delivering a presentation at the University of Birmingham.
\end{rSubsection}

\end{rSection}
\begin{rSection}{Specific Computational Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Operating Systems \ & Windows, Ubuntu \\
Programming Languages \ & Python, R, SQLite, Bash \\
Packages \ & Bioconductor, scikit-learn, matplotlib, ggplot2 \\
Related Tools \ & Git, BLAST, Linux HPC \\
General Software \ & MS Office, Latex  \\
\end{tabular}

\end{rSection}

\begin{rSection}{References}

\begin{center}
\setlength{\tabcolsep}{13pt}
\begin{tabular}{ccc} 
Dr Klaus F{\"u}tterer (Tutor) & Dr Marco Catoni & Dr Ralf Weber \\ 
Reader in Structural Biology & Lecturer in Plant Biology & Director of Bioinformatics \\ 
School of Biosciences & School of Biosciences & Phenome Centre Birmingham \\ 
University of Birmingham & University of Birmingham  & University of Birmingham \\
Edgbaston & Edgbaston & Edgbaston \\
B15 2TT & B15 2TT & B15 2TT \\
k.futterer@bham.ac.uk & m.catoni@bham.ac.uk & r.j.weber@bham.ac.uk \\
\end{tabular}
\end{center}
 
\end{rSection}
\end{document}
