\section{\faFlask}{Key Publications}

  \resumeEntryStart
    \resumeEntryTD
      {Multi-omics identify LRRC15 as a COVID-19 severity predictor and persistent pro-thrombotic signals in convalescence}{\href{https://doi.org/10.1101/2022.04.29.22274267}{Publication}, \href{https://github.com/jackgisby/covid-longitudinal-multi-omics/tree/main/notebooks}{GitHub}}
      
    \resumeItemListStart
      \resumeItem {Used inferential statistics, supervised learning and visualisations to derive biological insights from high-dimensional molecular measurements and clinical data.}
      \resumeItem {Mentored researchers to contribute to the processing and analysis of large biological datasets.}
    %   \resumeItem {Identified cell-specific networks of analytes that have dynamic trajectories following COVID-19 infection.}
    \resumeItemListEnd
    
    \resumeEntryTD
      {Longitudinal proteomic profiling of dialysis patients with COVID-19 reveals markers of severity and predictors of death}{\href{https://elifesciences.org/articles/64827}{Publication}, \href{https://github.com/jackgisby/longitudinal_olink_proteomics/blob/main/scripts/example_script.md}{GitHub}}
    \resumeItemListStart
      \resumeItem {Identified molecular changes that precede death from COVID-19 with mixed models and Cox regression.}
      \resumeItem {Disseminated findings to researchers of various disciplines, including at international conferences.}
    \resumeItemListEnd
    
    \resumeEntryTD
      {Mendelian randomisation identifies alternative splicing of the FAS death receptor as a mediator of severe COVID-19}{\href{https://www.medrxiv.org/content/10.1101/2021.04.01.21254789v1}{Preprint}}
    \resumeItemListStart
      \resumeItem {Developed a Nextflow pipeline to integrate genetic variants with expression quantitative trait loci.}
      \resumeItem {Determined potential drug targets for severe COVID-19 using causal inference.}
      \resumeItem {Used fine mapping in tandem with public data repositories to investigate variants that cause disease.}
    \resumeItemListEnd
    
    \resumeEntryTD
      {The widespread nature of Pack-TYPE transposons reveals their importance for plant genome evolution}{\href{https://journals.plos.org/plosgenetics/article?id=10.1371/journal.pgen.1010078}{Publication}, \href{https://github.com/jackgisby/packFinder}{GitHub}, \href{https://www.bioconductor.org/packages/release/bioc/html/packFinder.html}{Bioconductor}}
    \resumeItemListStart
      \resumeItem {Developed an R package for identifying rare DNA transposons that capture and reshuffle host DNA.}
      \resumeItem {Annotated elements in public sequence data to demonstrate their impact on the evolution of host genes.}
    \resumeItemListEnd
    
  \resumeEntryEnd
