\section{\faBriefcase}{Other Projects}

  \resumeEntryStart

    \resumeEntryTD
      {Deep learning for identifying anomalous chemicals}{\href{https://github.com/computational-metabolomics/deepmet}{GitHub}}
    \resumeItemListStart
      \resumeItem {Created a metabolite-likeness model using a transformer-based anomaly detection algorithm.}
      \resumeItem {Created a Python package with a command-line API for training and applying models to new data.}
      \resumeItem {Automated unit and integration testing, linting and code coverage checks with GitHub Actions.}
    \resumeItemListEnd

    \resumeEntryTD
      {A teaching resource for creating reproducible and shareable data pipelines}{\href{https://github.com/ImperialCollegeLondon/ReCoDE_rnaseq_pipeline}{GitHub}}
    \resumeItemListStart
      \resumeItem {Developed a resource to help teach students how to make reproducible pipelines for large datasets.}
      \resumeItem {Demonstrated Docker, Nextflow, version control, continuous integration and automated documentation.}
    \resumeItemListEnd

    \resumeEntryTD
      {A Python package for metabolite annotation}{\href{https://github.com/computational-metabolomics/metaboblend}{GitHub}}
    \resumeItemListStart
      \resumeItem {Created an efficient application to process high volumes of data using multiprocessing and profiling.}
      \resumeItem {Developed and optimised SQLite databases to store and efficiently query chemical data.}
    %   \resumeItem {Parallelised the annotation workflow on a high-performance computing cluster.}
    \resumeItemListEnd

    \resumeEntryTD
      {A cloud ETL pipeline for combining TfL transport records with weather data}{\href{https://github.com/jackgisby/tfl-bikes-data-pipeline}{GitHub}}
    \resumeItemListStart
      \resumeItem {Used Airflow to schedule the ingestion and integration of multiple datasets on the Google Cloud Platform.}
      \resumeItem {Used PySpark to distribute the processing of large datasets across a Dataproc cluster.}
      \resumeItem {Optimised an SQL (BigQuery) database using a star schema, indexing and time-based partitioning.}
    \resumeItemListEnd

  \resumeEntryEnd
