% get document settings
\include{config}

% determines what resume subtype to make
\newcommand{\resumeType}{bio}

\begin{document}

%---------------------------------------------------- HEADER ----------------------------------------------------

\headertype{\orcid}{\github}{}{\phone}{\email}{} % Set the order of items here
\vspace{-5pt} % Set a negative value to push the body up, and the opposite

\section{\faGears}{Statement}
 \vspace{3pt}
 \resumeEntryStart
  {\small Data scientist applying inferential statistics, supervised learning and visualisation to develop stories from data. Experienced in developing reproducible software to process and store large datasets. Demonstrated ability to collaborate with technical and subject matter experts to extract valuable insights. Looking to learn and grow in a fast-paced environment where my work can have an immediate impact.\par}
 \resumeEntryEnd


\section{\faPieChart}{Experience}
    
\resumeEntryStart
    \resumeEntryTSDL
    {Imperial College London}{August 2020 -- July 2023}
    {Doctoral Researcher}{London, UK}
    \resumeItemListStart
        \resumeItem {}
    \resumeItemListEnd
    
    \resumeEntryTSDL
    {The Binding Site}{Aug 2018 -- Aug 2019}
    {Industrial Placement}{Birmingham, UK}
    \resumeItemListStart
        \resumeItem {Took responsibility for the timely delivery of research and development projects and statistical reports.}
        \resumeItem {Communicated with, and delivered presentations to, a wide variety of interdisciplinary staff.}
    \resumeItemListEnd
\resumeEntryEnd

\section{\faGraduationCap}{Education}

  \resumeEntryStart
    \resumeEntryTSDL
      {Imperial College London}{Aug 2020 -- Aug 2023}
      {Computational Biology, PhD Candidate}{London, UK}
    %   Biomedical Data Science
  \vspace{6pt}
  
    \resumeEntryTSDL
      {University of Birmingham}{Sep 2016 -- Jul 2020}
      {Biochemistry with Professional Placement, MSci - First Class}{Birmingham, UK}
  \resumeEntryEnd


% \pagebreak

\section{\faGears}{Skills}
 \resumeEntryStart
  \resumeEntryS{Languages} {R, Python, Bash, SQL}
  \resumeEntryS{Packages} {pandas, multiprocessing, scikit-learn, PyTorch, caret, ggplot2, unittest, testthat}
  \resumeEntryS{Tools} {Git/GitHub, Docker, Conda, Nextflow, Airflow}  % Spark, Terraform
  \resumeEntryS{Compute} {High-performance computing clusters, exposure to the Google Cloud Platform}
  \resumeEntryS{Data} {Transcriptomics (bulk and single-cell RNA-seq), Proteomics (Olink and SomaLogic assays), Genomics (sequences and summary), Ontologies and Clinical data}
 \resumeEntryEnd

\vspace{5pt}


\section{\faFlask}{Selected Publications}

\resumeEntryStart
    % nature comms lrrc15
    \item \textbf{Jack S. Gisby}\textsuperscript{\textdagger}, Norzawani B. Buang\textsuperscript{\textdagger}, [...], David C. Thomas\textsuperscript{\textdagger}, James E. Peters\textsuperscript{\textdagger}. \textbf{Multi-omics identify falling LRRC15 as a COVID-19 severity marker and persistent pro-thrombotic signals in convalescence.} \textit{Nature Communications} 2022. \href{https://doi.org/10.1038/s41467-022-35454-4}{10.1038/s41467-022-35454-4}
      
    % elife proteomics
    \item \textbf{Jack S. Gisby}\textsuperscript{\textdagger}, Candice L Clarke\textsuperscript{\textdagger}, Nicholas Medjeral-Thomas\textsuperscript{\textdagger}, [...], Michelle Willicombe\textsuperscript{\textdagger}, David C Thomas\textsuperscript{\textdagger}, James E Peters\textsuperscript{\textdagger}. \textbf{Longitudinal proteomic profiling of dialysis patients with COVID-19 reveals markers of severity and predictors of death.} \textit{eLife} 2021. \href{https://doi.org/10.7554/eLife.64827}{10:e64827}
    
    % transposons 
    \item \textbf{Jack S. Gisby}, Marco Catoni. \textbf{The widespread nature of Pack-TYPE transposons reveals their importance for plant genome evolution.} \textit{PLOS Genetics} 2022. \href{https://doi.org/10.1371/journal.pgen.1010078}{10.1371/journal.pgen.1010078}
    
    % FAS preprint
    \item Lucija Klaric\textsuperscript{\textdagger}, \textbf{Jack S. Gisby}\textsuperscript{\textdagger}, Artemis Papadaki\textsuperscript{\textdagger}, [...], James F Wilson\textsuperscript{\textdagger}, James E Peters\textsuperscript{\textdagger}. \textbf{Mendelian randomisation identifies alternative splicing of the FAS death receptor as a mediator of severe COVID-19.} \textit{medRxiv} 2021. \href{https://doi.org/10.1101/2021.04.01.21254789 }{2021.04.01.21254789}
    
    \textdagger Equal contributions \hfill \orcidlink{https://orcid.org/0000-0003-0511-8123}{\hspace{0.3mm} \href{{https://orcid.org/0000-0003-0511-8123}}{orcid.org/0000-0003-0511-8123}}
    
\resumeEntryEnd

\section{\faBriefcase}{Other Projects}

  \resumeEntryStart

    \resumeEntryTD
      {A teaching resource for creating reproducible and shareable data pipelines}{\href{https://github.com/ImperialCollegeLondon/ReCoDE_rnaseq_pipeline}{GitHub}}
    \resumeItemListStart
      \resumeItem {Developed a resource to help teach students how to make reproducible pipelines for large datasets.}
      \resumeItem {Demonstrated Docker, Nextflow, version control, continuous integration and automated documentation.}
    \resumeItemListEnd

    \resumeEntryTD
      {A cloud ETL pipeline for combining TfL transport records with weather data}{\href{https://github.com/jackgisby/tfl-bikes-data-pipeline}{GitHub}}
    \resumeItemListStart
      \resumeItem {Used Airflow to schedule the ingestion and integration of multiple datasets on the Google Cloud Platform.}
      \resumeItem {Used PySpark to distribute the processing of datasets across a Dataproc cluster.}
      \resumeItem {Optimised an SQL (BigQuery) database using indexing and time-based partitioning.}
    \resumeItemListEnd

  \resumeEntryEnd

\end{document}
