\section{\faPieChart}{Experience}
    
\resumeEntryStart
    \resumeEntryTSDL
    {Immunology and Inflammation, Imperial College London}{August 2020 -- July 2023}
    {Doctoral Researcher}{London, UK}
    \resumeItemListStart
        \resumeItem {Integrated proteomic, transcriptomic and genetic data to investigate disease pathology.}
        \resumeItem {Applied longitudinal models, network analyses and machine learning to high-dimensional datasets.}
        \resumeItem {Employed causal inference and colocalisation to understand disease-causing genetic variants.}
        \resumeItem {Used and developed Nextflow \& HPC-based pipelines to process sequence and variant data.}
        \resumeItem {Delivered lectures and workshops, and created \href{https://github.com/ImperialCollegeLondon/ReCoDE_rnaseq_pipeline}{teaching materials for data science \faGithub}.}
        \resumeItem {Disseminated research findings through peer-reviewed publications and conference presentations.}
    \resumeItemListEnd
    
    \resumeEntryTSDL
    {Biosciences, University of Birmingham}{July 2019 – July 2020}
    {Research volunteer}{Birmingham, UK}
    \resumeItemListStart
        \resumeItem {Developed an R/Bioconductor package for \href{https://bioconductor.org/packages/release/bioc/html/packFinder.html}{annotating rare transposons in genome sequences \faGithub}.}
        \resumeItem {Mined genome sequence data to uncover the impact of repetitive elements on the evolution of host genes.}
    \resumeItemListEnd

    \resumeEntryTSDL
    {Biosciences, University of Birmingham}{October 2019 – May 2020}
    {MSci Research}{Birmingham, UK}
    \resumeItemListStart
        \resumeItem {Developed a \href{https://github.com/jackgisby/metaboblend}{Python package for processing and annotation of LC-MS metabolomics data \faGithub}.}
        \resumeItem {Created a \href{https://github.com/jackgisby/deepmet}{deep learning-based anomaly detection model \faGithub} that classifies molecular structures.}
        \resumeItem {Adhered to software engineering best practices, including version control and automated testing.}
    \resumeItemListEnd

    \resumeEntryTSDL
    {The Binding Site}{Aug 2018 -- Jul 2019}
    {Industrial Placement}{Birmingham, UK}
    \resumeItemListStart
        \resumeItem {Took responsibility for the timely delivery of assay development projects and statistical reports.}
        \resumeItem {Communicated with, and delivered presentations to, a wide variety of interdisciplinary staff.}
    \resumeItemListEnd
\resumeEntryEnd

