\section{\faBriefcase}{Other Projects}

  \resumeEntryStart
    \resumeEntryTD
      {Using time series data to investigate COVID-19 pathogenesis}{\href{https://elifesciences.org/articles/64827}{Publication}, \href{https://github.com/jackgisby/longitudinal_olink_proteomics/blob/main/scripts/example_script.md}{GitHub}}
    \resumeItemListStart
      \resumeItem {Used linear mixed models and Cox regression to identify changes that precede death from COVID-19.}
      \resumeItem {Used random forests to classify disease severity and extract important predictors.}
      
    \resumeItemListEnd
    
    \resumeEntryTD
      {An R package for processing sequence data}{\href{https://journals.plos.org/plosgenetics/article?id=10.1371/journal.pgen.1010078}{Publication}, \href{https://github.com/jackgisby/packFinder}{GitHub}, \href{https://www.bioconductor.org/packages/release/bioc/html/packFinder.html}{Repository}}
    \resumeItemListStart
      \resumeItem {Developed an R package for mining text-based datasets, that averages ~1000 downloads each year.}
      \resumeItem {Made project available on an open-source repository with automated documentation, testing and linting.}
    \resumeItemListEnd
    
    \resumeEntryTD
      {A Python package for processing chemical data}{\href{https://github.com/computational-metabolomics/metaboblend}{GitHub}}
    \resumeItemListStart
      \resumeItem {Developed a package for processing chemicals, stored as graph data structures.}
      \resumeItem {Scraped data from public APIs to validate the performance of the package.}
    \resumeItemListEnd
    
    \resumeEntryTD
      {Causal inference applied to large genetic datasets}{\href{https://www.medrxiv.org/content/10.1101/2021.04.01.21254789v1}{Publication}}
    \resumeItemListStart
      \resumeItem {Created a parallelised pipeline using high performance computing clusters to process large (>1TB) datasets.}
      \resumeItem {Used causal inference methods to elucidate factors that may cause severe COVID-19.}
    \resumeItemListEnd
  \resumeEntryEnd
